Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix

### 2018-03-09 r1doc/RebuttalTetrahelixUntwistV2.tex

The equitetrabeam is introduced as a special case that the rail angle is zero. It is proposed that
transformation from tetrahelix to equitetrabeam is possible by changing the minimax ratio about
16\%.

Overall, this paper is acceptable, but requires some revision. The following includes some comments.

\subsection{Modification}
\begin{itemize}
\item
The sentences of this paper need to be compact. Please read several times and then clean
the sentences.
``without loss of generality'' $\rightarrow$ ``generally''
\highlighttext{The term ``without loss of generality'' is being used specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowed in a proof because of symmetry or an ability to make
  a choice that does not change the validity of the proof.
  However, because this was unclear to the reviewer, in order to clarify this, I have added the word ``assume'' to the first use of the phrase ``without loss of generality'' and the phrase ``By symmetry'' to the second use.
  }

\item
  The explanation for figure 8 can be erased by drawing the general case for figure 8.
  \highlighttext{Yes, you are correct, thank you, I have made the diagram (see \cref{fig:wobble}) more general and removed the
    disclaiming text.}
    \begin{figure}
     \centering
     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram2.png}
     \caption{Wobble Vectors from Non-Coincident Axes}
  \label{fig:wobble}
\end{figure}
  \item
    Instead of sentence starting to ‘we……’ , the passive sentence is recommended.
    \highlighttext{
      I believe editorial opinion is somewhat divided\cite{firstperson} on the use of the word ``we'' when it is used to mean ``the author and the reader together'' as I have used it. Most editors do not prefer passive sentences in general.
      Nonetheless, in deference to the reviewer, I have searched the paper for each use of the word ``we'' and
      removed it in most, but not all cases.
      }
    \item 
 The following sentence is obscure. You'd better suggest a way to measure optimality using
 some kinematic indices :
\begin{quote}
 We have not yet proved that a two-class tetrahelix is optimal, but it suffices to show
that there exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
\end{quote}

@@

This paper proposed a method to transform the BC helix to Planar-faced tetrahelix by minimizing the difference between the longest and shortest edges, under some constraints. The author tried to explain his finding logically, and the background of the research is explained well. Also, the author shared the materials for this research at github. I have some comments for this paper as follows:

\begin{enumerate}

  \item
 I can see the organization of this paper is as follows: 
 Intro (2pages) – A designer’s formulation for the BC helix(2 pages) – Optimal tetrahelices are triple helix(3 pages) – Parameterizing tetrahelices via rail angle(2 pages) – The inradius(0.5 pages) – The Equitetrabeam (0.5 pages) – An Untwisted continuum (0.5 pages) – Conclusion
 \item 
   I think the author tried to explain all the findings but I think the organization of the paper should be revised to be emphasized carefully. Even for the researchers in this field, I am not convinced the paper is clearly written to emphasize the contribution well. Some sections can be combined, and the organization should be changed to emphasize the major contribution of this paper. I think this is the most significant point to improve the readability of the paper.

   \highlighttext{
     In order to address this, I have added the sentence below at the end of the introduction.
     }

   \highlighttext {
The remainder of this  paper:
\begin{enumerate}
\item provides a new formulation for the BC helix that is more natural for engineers,
\item defines a concept of minimum maximum edge-length optimality that maintains
  the structure as close to regularity as possible,
  \item proves that all
    optimal tetrahelices are in fact triple helices,
\item provides formulae for constructing optimal tetrahelices of different twists or for optimally
    transforming a
    robot from a twisted to a planar configuration in a way that maintains optimum regularity,
\item gives a formula for the inradius of an optimal tetrahelix,
\item describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
  a structural beam or for applying standard robot gaits to a tetrahedral robot, and
\item discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
  \end{enumerate}
}

### 2018-03-09 r1doc/TetrahelixUntwistV2.tex
yet another update

The vertices of the tetrahedra lie upon
three helices about the central axis.
The 
Tetrobot\cite{readglussbot,TetrobotBook} uses the regularity of
this geometry to make a tentacle-like robot that can crawl like a slug
or mollusk.  These modular robotic systems use mechanical actuators which can
change their length, connected by special joints,
such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint or the CMS joint\cite{HamlinSandersonCMS}
used in the original Tetrobot.
This allows many members to meet in a single point.
Such machines can
follow purely regular mathematical models such as the Boerdijk-Coxeter
helix or the Octet Truss\cite{richard1961synergetic}.

@@

Imagining \cref{fig:closeup} or \cref{fig:closeuporthog} as a static mechanical structure,
observe that it is useful to the mechanical engineer
because the structure is a mechanically strong, inherently rigid,
omni-triangulated space frame.
Then imagine that each static edge is replaced with an
actuator that can dynamically become shorter or longer in response to electronic control,
and the vertices are joints that support sufficient angular displacement
for this to be possible. An example of such a machine is a Tetrobot,
shown in figs. [4] and \cref{fig:tetrobot}.

@@

\highlighttext{
The remainder of this  paper:
\begin{enumerate}
\item provides a new formulation for the BC helix that is more natural for engineers,
\item defines a concept of minimum maximum edge-length optimality that maintains
  the structure as close to regularity as possible,
  \item proves that all
    optimal tetrahelices are in fact triple helices,
\item provides formulae for constructing optimal tetrahelices of different twists or for optimally
    transforming a
    robot from a twisted to a planar configuration in a way that maintains optimum regularity,
\item gives a formula for the inradius of an optimal tetrahelix,
\item describes a completely planar tetrahelix (the \emph{equitetrabeam}) useful as
  a structural beam or for applying standarod robot gaits to a tetrahedral robot, and
\item discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
\end{enumerate}
}

@@

R.W. Gray's website\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in a more accessible form, gives the Cartesian coordinates $\begin{bmatrix}
           x \\
           y \\
           z
         \end{bmatrix}$
for a counter-clockwise BC Helix in a right-handed coordinate system:
\begin{equation}
  \label{graycoxeter}
\vec{V}(n) =
\left [
  \begin{tabular}{c}
   $ r_{bc} \cos{n \theta_{bc}} $\\
   $ r_{bc} \sin{n \theta_{bc}} $\\
   $ n h_{bc}  $
  \end{tabular}
  \right ],
\end{equation}
\text{where: \qquad}
  \begin{tabular}{l}
 $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $,\\
 $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $, and \\
 $ \theta_{bc} = \arccos(-2/3) $  \text{,}\\
  \end{tabular}

@@

\Cref{fig:helixcomparison} illustrates this difference with a 7-tetrahedra BC helix, which is
in fact the same geometry as the robot illustrated in \cref{fig:tetrobot}.
Although the vertices coincide,
 \cref{graycoxeter} evaluated
at real values generates the black helix which runs through every vertex, and \cref{eq:colored} defines
the red, yellow, and blue helices. In this figure,
these rail helices have been rendered at a slightly higher radius than the vertices for clarity;
in actuality, the maximum distance between the continuous, curved helix and the
straight edges between vertices is much smaller than can be clearly rendered.

@@

\highlighttext{
As engineers and roboticists it is desirable to design tetrahelices that
are slightly irregular that ``untwist'' the BC Helix in an optimal way.
For machines
made out of linear actuators with limited range of extension,
the best definition of optimality is to minimize the difference in
lengths between the shortest and longest members in the robot of a given radius.
By maintaining all lengths as close to the same ``regular'' length as possible,
such as the mean length of the actuator,
one retains the greatest possible freedom of motion for the robot.
}

\highlighttext{
This paper use the term \emph{tetrahelix} to mean any structure physically constructible of
vertices and finite edges which is isomorphic to the BC helix, but with possibly different edge lengths,
and in which the
vertices lie on three helices (red, blue, and yellow, or ($R,B,Y$)). 
Mathematically, this structure extends
without bound, although physical robots or variable geometry trusses will
be truncations of such a structure.
This idea is captured by a function $T$ that gives the length between any
two nodes that are connected, and undefined ($\perp$) when not connected :
$T(n_1,n_2) : \mathbb{Z} \times \mathbb{Z} \mapsto \mathbb{R} \cup \{\perp\} $.
To describe a physically realizable machine, the function $T$ representing a tetrahelix
is constrained:
$(\forall n_1,n_2 : T(n_1,n_2) > 0)$.
For a BC Helix, $(\forall x,y : T(x,y) \neq \perp \Rightarrow T(x,y) = 1)$.
}

@@

\highlighttext{
  The ratio of the BC Helix is 1: $ R(H_{BC}) = 1$.
  }
\highlighttext{
A \emph{triple helix} is three congruent helices that share an axis. The remainder of this
section proves that
optimal tetrahelices are in fact triple helices.
In stages, this section proves that the helices in optimal tetrahelices:
\begin{enumerate}
\item have the same pitch,
\item have parallel axes,
\item share the same axis,
\item have the same radius,
  \item have the same rail length,
  \item have axially equidistant vertices, and therefore
  \item are in fact triple helices.
\end{enumerate}
The formula for radius that optimizes the tetrahelix for a given rail angle
is the result of the \cref{sec:parameterizing}.
}

@@

Since the axes are parallel, one may define the \emph{inradius}, represented by the letter $i$, of a
tetrahelix to be the radius of the largest
cylinder parallel to this axis that is surrounded by each tetrahelix and penetrated by no edge.

@@

 Because the equitetrabeam which has a rail angle of $0$ still has
 chirality, that is, one still must decide to connect the one-hop edge to
 the clockwise or the counter-clockwise vertex, it is not possible to build
 a smooth continuum where $\rho$ transitions from positive to negative
 which remains optimal. One can use a negative $\rho$ in $\vec{H}_{general}$
 but it does not produce minimax optimal tetrahelices. In other words,
 untwisting a counter-clockwise tetrahelix to rail angle $0$ and then going
even further does produce a clockwise tetrahelix, but one in which the
 one-hop and two-hop lengths in the wrong places, that is, two-hop
 becomes shorter than one-hop.
 Likewise, $\rho > \rho_{bc}$ generates
 a tetrahelix, but \highlighttext{its optimality has not proved or investigated} in that range.

@@

The curvature of a rail helix is formally given by:
\begin{equation}
  \frac{|r_{\rho}|}{r_{\rho}^2 + (d_{\rho}/\rho)^2} \text{ .}
\end{equation}
which goes to $0$ as $\rho$ approaches $0$ (the equitetrabeam.)
As $\rho$ increase up to $\rho_{bc}$ the curvature increases smoothly until the BC Helix is reached.

Perhaps surprisingly, the optimal untwisting is accomplished only by
changing the length of the two-hop member, leaving the one-hop member
and rail length equivalent within this continuum.\footnote{Before
deriving  \cref{eqrhoopt}, \highlighttext{a continuum was created} by
using a linear interpolation between the optimal radius for the
equitetrabeam and the BC Helix. This minimax optimum of this simpler
approach was at most 1\% worse than the optimum computed by
\cref{eqrhoopt}.}
 However, it should
be noted that an engineer or architect may also use $\vec{H}_{general}$ 
directly and interactively via \url{https://pubinv.github.io/tetrahelix/},
and that minimax length optimality is a
mathematical starting point rather than the final word on the beauty and utility of
physical structures. For example, a structural engineer might increase a
radius past optimality in order to resist buckling.
%% Add a figure here of a deep beam and of an arch.

@@

It is proven there exists a continuum of minimax edge-length optimal tetrahelices
having as one end the completely regular Boerdijk-Coxeter Helix and at the
other end a completely untwisted tetrahelix with equilateral cross
section and planar faces, the equitetrabeam.
By changing the length of only one out of three members by less than $16\%$,
all configurations in the continuum may be reached.
All such optimal tetrahelices may provably be generated by a
simple equation giving coordinates or by
selecting appropriate edge lengths generated from the same equation. 
A machine, such as \highlighttext{the} Tetrobot or a variable-geometry truss \highlighttext{ depicted in \cref{fig:tetrobot}}, that can change
the length of some of its members by $16\%$ can thus twist and untwist itself.
A completely regular Tetrobot can untwist itself to create a planar
face on the ground for locomotion \highlighttext{via standard gaits}.
With a numeric solution, a designer may choose
a rotation angle to obtain an optimal tetrahelix design
of any pitch, including rational ones.

>>>>

The vertices of the tetrahedra lie upon
three helices about the central axis.
The 
Tetrobot\cite{readglussbot,TetrobotBook} uses the regularity of
this geometry to make a tentacle-like robot that can crawl like a mollusk.
These modular robotic systems use mechanical actuators which can
change their length, connected by special joints,
such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint or the CMS joint\cite{HamlinSandersonCMS}
used in the original Tetrobot.
This allows many members to meet in a single point.
Such machines can
follow purely regular mathematical models such as the Boerdijk-Coxeter
helix or the octet truss\cite{richard1961synergetic}.

@@

Imagining \cref{fig:closeup} or \cref{fig:closeuporthog} as a static mechanical structure,
observe that it is useful to the mechanical engineer
because the structure is a mechanically strong, inherently rigid,
omni-triangulated space frame.
Then imagine that each static edge is replaced with an
actuator that can dynamically become shorter or longer in response to electronic control,
and the vertices are joints that support sufficient angular displacement
for this to be possible. An example of such a machine is a Tetrobot,
shown in fig. 4 and \cref{fig:tetrobot}.

@@

\highlighttext{
The remainder of this  paper:
\begin{enumerate}
\item provides a new formulation for the BC helix that is more natural for engineers,
\item defines a concept of minimum maximum edge-length optimality that maintains
  the structure as close to regularity as possible,
  \item proves that all
    optimal tetrahelices are in fact triple helices,
\item provides formulae for constructing optimal tetrahelices of different twists or for optimally
    transforming a
    robot from a twisted to a planar configuration in a way that maintains optimum regularity,
\item gives a formula for the inradius of an optimal tetrahelix,
\item describes a completely planar tetrahelix (the \emph{equitetrabeam}) useful as
  a structural beam or for applying standarod robot gaits to a tetrahedral robot, and
\item discusses the continuum of optimal tetrahelices between the BC helix and equitetrabeam.
\end{enumerate}
}

@@

R.W. Gray's website\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in a more accessible form, gives the Cartesian coordinates $\begin{bmatrix}
           x \\
           y \\
           z
         \end{bmatrix}$
for a counter-clockwise BC helix in a right-handed coordinate system:
\begin{equation}
  \label{graycoxeter}
\vec{V}(n) =
\left [
  \begin{tabular}{c}
   $ r_{bc} \cos{n \theta_{bc}} $\\
   $ r_{bc} \sin{n \theta_{bc}} $\\
   $ n h_{bc}  $
  \end{tabular}
  \right ],
\end{equation}
\text{where: \qquad}
  \begin{tabular}{l}
 $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $,\\
 $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $, and \\
 $ \theta_{bc} = \arccos(-2/3) $  \text{,}\\
  \end{tabular}

@@

\Cref{fig:helixcomparison} illustrates this difference with a 7-tetrahedra BC helix, which is
in fact the same geometry as the robot illustrated in \cref{fig:tetrobot}.
Although the vertices coincide,
 \cref{graycoxeter} evaluated
at real values generates the black helix which runs through every vertex, and \cref{eq:colored} defines
the red, yellow, and blue helices. In this figure,
these \highlighttext{continuous} rail helices have been rendered at a slightly higher radius than the vertices for clarity;
in actuality, the maximum distance between the continuous, curved helix and the
straight edges between vertices is much smaller than can be clearly rendered.

@@

\highlighttext{
As engineers and roboticists it is desirable to design tetrahelices that
are slightly irregular that ``untwist'' the BC helix in an optimal way.
For machines
made out of linear actuators with limited range of extension,
the best definition of optimality is to minimize the difference in
lengths between the shortest and longest members in the robot of a given radius.
By maintaining all lengths as close to the same ``regular'' length as possible,
such as the mean length of the actuator,
one retains the greatest possible freedom of motion for the robot.
}

\highlighttext{
This paper use the term \emph{tetrahelix} to mean any structure physically constructible of
vertices and finite edges which is isomorphic to the BC helix, but with possibly different edge lengths,
and in which the
vertices lie on three helices (red, blue, and yellow, or ($R,B,Y$)). 
Mathematically, this structure extends
without bound, although physical robots or variable geometry trusses will
be truncations of such a structure.
This idea is captured by a function $T$ that gives the length between any
two nodes that are connected, and undefined ($\perp$) when not connected :
$T(n_1,n_2) : \mathbb{Z} \times \mathbb{Z} \mapsto \mathbb{R} \cup \{\perp\} $.
To describe a physically realizable machine, the function $T$ representing a tetrahelix
is constrained:
$(\forall n_1,n_2 : T(n_1,n_2) > 0)$.
For a BC helix, $(\forall x,y : T(x,y) \neq \perp \Rightarrow T(x,y) = 1)$.
}

@@

\highlighttext{
  The ratio of the BC helix is 1: $ R(H_{BC}) = 1$.
  }
\highlighttext{
A \emph{triple helix} is three congruent helices that share an axis. The remainder of this
section proves that
optimal tetrahelices are in fact triple helices.
In stages, this section proves that the helices in optimal tetrahelices:
\begin{enumerate}
\item have the same pitch,
\item have parallel axes,
\item share the same axis,
\item have the same radius,
  \item have the same rail length,
  \item have axially equidistant vertices, and therefore
  \item are in fact triple helices.
\end{enumerate}
The formula for radius that optimizes the tetrahelix for a given rail angle
is the result of the \cref{sec:parameterizing}.
}

@@

Since the axes are parallel, one may define the \emph{inradius}, represented by \highlighttext{$r_{in}$}, of a
tetrahelix to be the radius of the largest
cylinder parallel to this axis that is surrounded by each tetrahelix and penetrated by no edge.

@@

 Because the equitetrabeam which has a rail angle of $0$ still has
 chirality, that is, one still must decide to connect the one-hop edge to
 the clockwise or the counter-clockwise vertex, it is not possible to build
 a smooth continuum where $\rho$ transitions from positive to negative
 which remains optimal. One can use a negative $\rho$ in $\vec{H}_{general}$
 but it does not produce minimax optimal tetrahelices. In other words,
 untwisting a counter-clockwise tetrahelix to rail angle $0$ and then going
even further does produce a clockwise tetrahelix, but one in which the
 one-hop and two-hop lengths in the wrong places, that is, two-hop
 becomes shorter than one-hop.
 Likewise, $\rho > \rho_{bc}$ generates
 a tetrahelix, but \highlighttext{its optimality has not been proved or investigated} in that range.

@@

The curvature of a rail helix is formally given by:
\begin{equation}
  \frac{|r_{\rho}|}{r_{\rho}^2 + (d_{\rho}/\rho)^2} \text{ .}
\end{equation}
which goes to $0$ as $\rho$ approaches $0$ (the equitetrabeam.)
As $\rho$ increase up to $\rho_{bc}$ the curvature increases smoothly until the BC helix is reached.

Perhaps surprisingly, the optimal untwisting is accomplished only by
changing the length of the two-hop member, leaving the one-hop member
and rail length equivalent within this continuum.\footnote{Before
deriving  \cref{eqrhoopt}, \highlighttext{a continuum was created} by
using a linear interpolation between the optimal radius for the
equitetrabeam and the BC helix. This minimax optimum of this simpler
approach was at most 1\% worse than the optimum computed by
\cref{eqrhoopt}.}
 However, it should
be noted that an engineer or architect may also use $\vec{H}_{general}$ 
directly and interactively via \url{https://pubinv.github.io/tetrahelix/},
and that minimax length optimality is a
mathematical starting point rather than the final word on the beauty and utility of
physical structures. For example, a structural engineer might increase a
radius past optimality in order to resist buckling.
%% Add a figure here of a deep beam and of an arch.

@@

It is proven there exists a continuum of minimax edge-length optimal tetrahelices
having as one end the completely regular Boerdijk-Coxeter helix and at the
other end a completely untwisted tetrahelix with equilateral cross
section and planar faces, the equitetrabeam.
By changing the length of only one out of three members by less than $16\%$,
all configurations in the continuum may be reached.
All such optimal tetrahelices may provably be generated by a
simple equation giving coordinates or by
selecting appropriate edge lengths generated from the same equation. 
A machine, such as \highlighttext{the} Tetrobot or a variable-geometry truss \highlighttext{ depicted in \cref{fig:tetrobot}}, that can change
the length of some of its members by $16\%$ can thus twist and untwist itself.
A completely regular Tetrobot can untwist itself to create a planar
face on the ground for locomotion \highlighttext{via standard gaits}.
With a numeric solution, a designer may choose
a rotation angle to obtain an optimal tetrahelix design
of any pitch, including rational ones.
